The emotion--facial expression link: Evidence from human and automatic expression recognition

### 2020-11-06 manuscript/manuscript_apa.Rmd
osf link

The R code and relevant data for statistical computing are available on the "The emotion–facial expression link (data and code)" repository from the Center for Open Science [@Dupré_Tcherkassof_2020].

>>>>

The R code and relevant data for statistical computing are available on *The emotion–facial expression link (data and code)* repository from the Center for Open Science at https://osf.io/erua5/ [@Dupré_Tcherkassof_2020].

### 2020-11-06 manuscript/manuscript_apa.tex
osf link

The R code and relevant data for statistical computing are available on the ``The emotion--facial expression link (data and code)'' repository from the Center for Open Science (Dupré \& Tcherkassof, 2020).

>>>>

The R code and relevant data for statistical computing are available on \emph{The emotion--facial expression link (data and code)} repository from the Center for Open Science at \url{https://osf.io/erua5/} (Dupré \& Tcherkassof, 2020).
